### 2013-09-15 results.tex
path metrics tabulated

>>>>

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated.

\input{tab_path_data}
